How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-03 tse-paper/content.tex
fix comments, move todos to code

% Todo: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques
exist 2) we implement (for a lack of readily available implementations)
and compare the most promising ones 3) we draw conclusions for when to
use which technique

% TODO: Include term predictive CI, link to FB paper and
https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

% TODO: What about the alternate solution, installing plugins to report
precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

% TODO It would be futile to compare our techniques with one of the
existing manual regex parsers, as (a) as our literature survey showed,
their scope is mainly limited to the Java ecosystem and (b) whether
they would work or not would be randomly based on whether the project
we select exhibits features their regular expressions were trained for.
Finally, they are not really automatic

@@

% At the moment there is only anecdotal evidence on the performance
of these
% techniques and on when a technique should be preferred over other
alternatives.
% Developers and researches currently have little support when choosing
which
% technique to use for a task.

% The goal of this article is to investigate different chunk retrieval
techniques
% for build logs and describe under which circumstances certain techniques
can be
% recommended over others.
% We aim to characterize different chunk retrieval techniques.
% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
criteria
% influence the suitability of a chunk retrieval technique for CI
build logs.

@@

* Try:
  \end{lstlisting}
  \caption{Example of a log chunk explaining why an Android/Gradle
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example-1}
\end{figure}

@@

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
--- FAIL: TestSeparator (0.03s)
    repo\_test.go:75: expected entry to be in form of `* [link] -
    description.`, got '* ...
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk.
%\todo{which build tool?}
%  \todo{move to where structural category explanation}
}
  \label{lst:chunk-example-3}
\end{figure}

@@

% \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
to retrieve information from continuous integration build logs.
% \textbf{RQ2} is refined into sub-questions along with the criteria
resulting from \textbf{RQ1} and compares their instantiations for the
three techniques:
% how many training examples a technique needs to perform best
(\textbf{RQ2.1}), how structurally diverse the examples can
be (\textbf{RQ2.2}) and how accurate the retrieved output is
(\textbf{RQ2.3}).
% To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
which encompasses about 800 log files from 80 repositories.
% Each log is labeled with the log part describing the reason a build
failed, keywords to search for this log part and a categorization of
the labeled log part according to its structural representation within
the log.

@@

% \noindent
% \textbf{Our work contributes:}
% \begin{itemize}
%   \item A tool with three prototypical implementations of chunk
retrieval techniques:
%	  \begin{itemize}
%	    \item program synthesis from examples using the Microsoft
PROSE library (PBE),
%	    \item a common information retrieval approach using text
similarity (CTS), and
%	    \item a keyword search approach (KWS).
%	  \end{itemize}
%   \item Recommendations for the configuration of each of the
investigated chunk retrieval techniques.
%   \item Guidelines on choosing a suitable chunk retrieval technique.
% \end{itemize}

@@

The first goal in analyzing system log files is ubiquitously to
separate constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output of a log
parser is an ordered list of timed events and their corresponding
parameter values~\cite{he2016evaluation}.
This structured log is then
the input to various machine learning and data mining processes.
%Researchers mine patterns for operational
%profiling~\cite{nagappan2009efficiently},
%debugging~\cite{oliner2012advances}, performance analytics or anomaly
%detection~\cite{nagappan2010abstracting}.
Xu et
%al.~\cite{xu2009detecting} leverage the connection of log statements
%to the source code producing them to separate messages into constant
%and variable parts more accurately.

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
%Classic log parsers interpret the whole log file into a sequence of
%events.
A similar approach could also be applied to build logs to
%determine the sequence of executed build steps or phases.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.
by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
% \section{Information Extraction and Retrieval Techniques} The
% techniques we investigate are based on existing methods of
% Programming by Example.%, information extraction and information
% retrieval.
This section presents different Programming by Example
% resources surrounding the PROSE library.
We explain its generic
% program synthesis algorithm and how PROSE synthesizes text
% extraction programs, the foundation of PBE\@.

@@

\subsubsection{FlashExtract: Data Extraction by Example}
Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
for the Microsoft PROSE framework.
% It enables a user to define text extraction programs for text,
% websites and spreadsheets by giving I/O examples.
FlashExtract's instantiation for text synthesizes extraction programs
from semi-structured text based on regular expressions.
Users can
extract multiple fields and structure them with hierarchy and
sequence.
% FlashExtract synthesizes programs to extract each of the fields
% leveraging the information about hierarchical containment and
% sequentiality.
It eliminates the need for the user to understand the
% entire structure of the processed document and decreases the effort
% of developing a suitable extraction program.

@@

With the term \textit{configuration,} we abstract over the training
and parametrization that different techniques require in different
forms.
A configuration can be explicitly stated or implicitly dervied
by learning through provided examples.
It is therefore a manual
specification of which information the chunk retrieval should target.
It also supplies the necessary information for the technique to
identify the targeted information chunk in a build log.
Each chunk
retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
smallest piece of text it can return (e.g., a line, or a word).
The
granularity might be adjustable by configuration.
\emph{Running a
chunk retrieval technique} means to execute a fully configured
technique to consumes as input a build log in plain text format and to
produce an array as output.
The array consists of substrings of the
build log text.

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:expl-pbe}
% \emph{Programming by Example} is a technique which synthesizes
% programs according to in- and output examples provided by the user.
% It enables users to create programs without a priori programming
% knowledge~\cite{mayer2015user}.
In the context of text extraction
% through regular expressions, Programming by Example relieves the
% developer from having to understand the whole document structure to
% solve a single extraction task~\cite{le2014flashextract:}.
In this
% work, we refer to our interpretation of Programming by Example as
% \emph{PBE}\@.
We investigate the suitability of PBE to retrieve
% information chunks from build logs.
In the following, we explain the
% configuration and application of PBE to chunk retrieval from CI
% build logs.

% TODO later: we should make sure to at least mention PROSE
% _somewhere_, it's crucial for why PBE is how it is
\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The
\emph{input} is the text of the build log file.
The \emph{output} is
an array of substrings of the log file text, representing the
substrings that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The
PROSE program synthesis then tries to construct a program consistent
with all training examples.
% A program is consistent with an example if it returns the defined
% output when executed on the defined
% input~\cite{mitchell1982generalization}.
PBE reports an error back to the user if it could not synthesize a
consistent program.
% The program synthesis builds on the FlashExtract DSL, which in turn
% uses the FlashMeta algorithm.
Both are described in
% Section~\ref{sec:rw-prose}.

% TODO Moritz: you said: The following is very obvious and could apply
to any
% technique.

% kinda.
It does give a descriptive error message on no match (and
% that is not possible in other techniques)
% otherwise yes, nothing interesting happens in the application of pbe
% though for consistency we might need this section? or merge
config/application?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
% Text Similarity approaches are used to filter unstructured textual
% software
%
artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
% One common and simple technique is the Vector Space Model.
We
% investigate when text similarity is a suitable technique to retrieve
% information chunks from build logs.
In the following we will explain
% the concept of how we apply text similarity to information retrieval
% from CI build logs, which we refer to as \emph{CTS}\@.

\subsubsection{Configuration}
To configure chunk retrieval though text similarity we chose to use
the same concept of examples as for PBE
% TODO Moritz: your question was: More details on this.
How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows.
The
lines of the output strings of the training examples define our search
query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad-hoc approach they
use is to search for related keywords.
Indeed, this was one of the
most common approaches we took when searching for the reason the build
failed within a log while creating the \emph{LogChunks} data
set~\cite{brandt2020logchunks}.
% As this is a technique readily available in many tools developers
% use to view build logs, we study when such a keyword search is
% suitable for retrieving information chunks from CI build logs.
In
% the following we will explain how we use simple keyword search to
% retrieve information from CI build logs, which we refer to as
% \emph{KWS}\@.

@@

% TODO Moritz: you said: some more details here?
% I would not know of any details to add.
It's really all we are doing

\subsection{Other Techniques}
%Literature mentions further build log analysis techniques.
This
%section describes them with our notion of chunk retrieval techniques.

@@

\noindent
\textbf{Training and Test Set}
We use \emph{LogChunks} as the data set for our study.
For each of the
80 repositories in it, \emph{LogChunks} contains 10 build logs,
manually labeled with the \emph{chunk} describing the
reason the build failed.
Additionally, it contains (1) keywords useful
to identify the substring in the log  and (2) which structural category
the substring belongs to.
% TODO Moritz: You said: Add details how key words were extracted.
Add example?
% how the keywords were put in logchunks does not fit here, that is
% maybe answered 2 paragraphs above already?
% how KWS uses the keywords is already described in the section
% introducing the technique => I would scrap everything but the first
% sentence directly above here :)

% TODO Moritz: You said: Add more details.
How was the split in numbers?
% this is described in the following paragraph, should we merge them
% (bc there are also no sub-RQs now) or is it close enough? :)
For each repository in \emph{LogChunks}, we split the examples
chronologically into training and test set.
Therefore, we train on
examples from past build logs and test on more recent build logs.

@@

% Recall and precision of CTS and KWS vary with the number of lines
% selected for retrieval.
We evaluate the effect of varying the number
% of extracted lines by multiplying the average number of lines
% present in the training examples with a \emph{retrieval size factor}
% from 0.5 to 2.5 in steps of 0.5.

@@

% The averaged precision, recall and F$_{1}$-score f all techniques is
% compared in Figure~\ref{fig:recall-precision-all}.
The recall of PBE
% has a high skew towards one and zero, meaning in most cases either
% the retrieval is successful or no relevant lines are extracted at
% all.
PBE has the highest average precision with 95\%.
Chunk
% retrieval with CTS has the highest average F$_{1}$-score with 51\%
% and the second highest recall with 46\%.
KWS has the smallest
% precision of the three chunk retrieval techniques.
With 16\% it is
% still higher than the precision of the RLR baseline with 7\%.
KWS
% has the highest recall of all techniques with 70\%.

@@

\section{Future Work}
\todo{survey build logs tools in industry}

>>>>

% Todo: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques
% exist 2) we implement (for a lack of readily available implementations)
% and compare the most promising ones 3) we draw conclusions for when to
% use which technique

% TODO: Include term predictive CI, link to FB paper and
% https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

% TODO: What about the alternate solution, installing plugins to report
% precise data? Ie., maven plugins
% - Lots of effort
% - not a generic solution
% - how to analyze history where such plugins were not installed
% - unclear which information you want

% TODO It would be futile to compare our techniques with one of the
% existing manual regex parsers, as (a) as our literature survey showed,
% their scope is mainly limited to the Java ecosystem and (b) whether
% they would work or not would be randomly based on whether the project
% we select exhibits features their regular expressions were trained for.
% Finally, they are not really automatic

@@

% % At the moment there is only anecdotal evidence on the performance
% of these
% % techniques and on when a technique should be preferred over other
% alternatives.
% % Developers and researches currently have little support when choosing
% which
% % technique to use for a task.

% % The goal of this article is to investigate different chunk retrieval
% techniques
% % for build logs and describe under which circumstances certain techniques
% can be
% % recommended over others.
% % We aim to characterize different chunk retrieval techniques.
% % For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which
% criteria
% % influence the suitability of a chunk retrieval technique for CI
% build logs.

@@

* Try:
  \end{lstlisting}
  \caption{Example of a log chunk explaining why an Android/Gradle
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example-1}
\end{figure}

@@

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
--- FAIL: TestSeparator (0.03s)
    repo\_test.go:75: expected entry to be in form of `* [link] - description.`, got '* ...
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk.
% TODO: which build tool?
% TODO: move to where structural category explanation
}
  \label{lst:chunk-example-3}
\end{figure}

@@

% % \textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited
% to retrieve information from continuous integration build logs.
% % \textbf{RQ2} is refined into sub-questions along with the criteria
% resulting from \textbf{RQ1} and compares their instantiations for the
% three techniques:
% % how many training examples a technique needs to perform best
% (\textbf{RQ2.1}), how structurally diverse the examples can
% be (\textbf{RQ2.2}) and how accurate the retrieved output is
% (\textbf{RQ2.3}).
% % To evaluate PBE, CTS and KWS we use the \emph{LogChunks} data set,
% which encompasses about 800 log files from 80 repositories.
% % Each log is labeled with the log part describing the reason a build
% failed, keywords to search for this log part and a categorization of
% the labeled log part according to its structural representation within
% the log.

@@

% % \noindent
% % \textbf{Our work contributes:}
% % \begin{itemize}
% %   \item A tool with three prototypical implementations of chunk
% retrieval techniques:
% %	  \begin{itemize}
% %	    \item program synthesis from examples using the Microsoft
% PROSE library (PBE),
% %	    \item a common information retrieval approach using text
% similarity (CTS), and
% %	    \item a keyword search approach (KWS).
% %	  \end{itemize}
% %   \item Recommendations for the configuration of each of the
% investigated chunk retrieval techniques.
% %   \item Guidelines on choosing a suitable chunk retrieval technique.
% % \end{itemize}

@@

The first goal in analyzing system log files is ubiquitously to
separate constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output of a log
parser is an ordered list of timed events and their corresponding
parameter values~\cite{he2016evaluation}.
This structured log is then
the input to various machine learning and data mining processes.
%Researchers mine patterns for operational
%profiling~\cite{nagappan2009efficiently},
%debugging~\cite{oliner2012advances}, performance analytics or anomaly
%detection~\cite{nagappan2010abstracting}.
% Xu et
%al.~\cite{xu2009detecting} leverage the connection of log statements
%to the source code producing them to separate messages into constant
%and variable parts more accurately.

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
%Classic log parsers interpret the whole log file into a sequence of
%events.
% A similar approach could also be applied to build logs to
%determine the sequence of executed build steps or phases.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.
by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

\subsection{Program Synthesis by Example}
\label{sec:rw-prose}
% % \section{Information Extraction and Retrieval Techniques} The
% % techniques we investigate are based on existing methods of
% % Programming by Example.%, information extraction and information
% % retrieval.
% This section presents different Programming by Example
% % resources surrounding the PROSE library.
% We explain its generic
% % program synthesis algorithm and how PROSE synthesizes text
% % extraction programs, the foundation of PBE\@.

@@

\subsubsection{FlashExtract: Data Extraction by Example}
Le et al.~\cite{le2014flashextract:} developed FlashExtract as a DSL
for the Microsoft PROSE framework.
% It enables a user to define text extraction programs for text,
% websites and spreadsheets by giving I/O examples.
FlashExtract's instantiation for text synthesizes extraction programs
from semi-structured text based on regular expressions.
Users can
extract multiple fields and structure them with hierarchy and
sequence.
% FlashExtract synthesizes programs to extract each of the fields
% leveraging the information about hierarchical containment and
% sequentiality.
% It eliminates the need for the user to understand the
% entire structure of the processed document and decreases the effort
% of developing a suitable extraction program.

@@

With the term \textit{configuration}, we abstract over the training
and parametrization that different techniques require in different
forms.
A configuration can be explicitly stated or implicitly dervied
by learning through provided examples.
It is therefore a manual
specification of which information the chunk retrieval should target.
It also supplies the necessary information for the technique to
identify the targeted information chunk in a build log.
Each chunk
retrieval technqiue has a specific \textit{granularity}, i.e.,\ the
smallest piece of text it can return (e.g., a line, or a word).
The
granularity might be adjustable by configuration.
\emph{Running a
chunk retrieval technique} means to execute a fully configured
technique to consumes as input a build log in plain text format and to
produce an array as output.
The array consists of substrings of the
build log text.

@@

\subsection{Program Synthesis by Example (PBE)}
\label{sec:expl-pbe}
% % \emph{Programming by Example} is a technique which synthesizes
% % programs according to in- and output examples provided by the user.
% % It enables users to create programs without a priori programming
% % knowledge~\cite{mayer2015user}.
% In the context of text extraction
% % through regular expressions, Programming by Example relieves the
% % developer from having to understand the whole document structure to
% % solve a single extraction task~\cite{le2014flashextract:}.
% In this
% % work, we refer to our interpretation of Programming by Example as
% % \emph{PBE}\@.
% We investigate the suitability of PBE to retrieve
% % information chunks from build logs.
% In the following, we explain the
% % configuration and application of PBE to chunk retrieval from CI
% % build logs.

% TODO later: we should make sure to at least mention PROSE
% _somewhere_, it's crucial for why PBE is how it is
\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example, we refer to them in short as \emph{examples}.
The
\emph{input} is the text of the build log file.
The \emph{output} is
an array of substrings of the log file text, representing the
substrings that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The
PROSE program synthesis then tries to construct a program consistent
with all training examples.
% % A program is consistent with an example if it returns the defined
% % output when executed on the defined
% % input~\cite{mitchell1982generalization}.
% PBE reports an error back to the user if it could not synthesize a
% consistent program.
% % The program synthesis builds on the FlashExtract DSL, which in turn
% % uses the FlashMeta algorithm.
% Both are described in
% % Section~\ref{sec:rw-prose}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.

% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
% % Text Similarity approaches are used to filter unstructured textual
% % software
% %
% artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
% % One common and simple technique is the Vector Space Model.
% We
% % investigate when text similarity is a suitable technique to retrieve
% % information chunks from build logs.
% In the following we will explain
% % the concept of how we apply text similarity to information retrieval
% % from CI build logs, which we refer to as \emph{CTS}\@.

\subsubsection{Configuration}
To configure chunk retrieval though text similarity we chose to use
the same concept of examples as for PBE
% TODO Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows.
The
lines of the output strings of the training examples define our search
query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

\subsection{Keyword Search (KWS)}
\label{sec:expl-skws}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad-hoc approach they
use is to search for related keywords.
Indeed, this was one of the
most common approaches we took when searching for the reason the build
failed within a log while creating the \emph{LogChunks} data
set~\cite{brandt2020logchunks}.
% As this is a technique readily available in many tools developers
% use to view build logs, we study when such a keyword search is
% suitable for retrieving information chunks from CI build logs.
% In
% the following we will explain how we use simple keyword search to
% retrieve information from CI build logs, which we refer to as
% \emph{KWS}\@.

@@

% TODO Moritz: you said: some more details here?
% I would not know of any details to add.
%It's really all we are doing

\subsection{Other Techniques}
%Literature mentions further build log analysis techniques.
%This
%section describes them with our notion of chunk retrieval techniques.

@@

\noindent
\textbf{Training and Test Set}
We use \emph{LogChunks} as the data set for our study.
For each of the
80 repositories in it, \emph{LogChunks} contains 10 build logs,
manually labeled with the \emph{chunk} describing the
reason the build failed.
Additionally, it contains (1) keywords useful
to identify the substring in the log  and (2) which structural category
the substring belongs to.
% TODO Moritz: You said: Add details how key words were extracted.
% Add example?
% how the keywords were put in logchunks does not fit here, that is
% maybe answered 2 paragraphs above already?
% how KWS uses the keywords is already described in the section
% introducing the technique => I would scrap everything but the first
% sentence directly above here :)

% TODO Moritz: You said: Add more details.
% How was the split in numbers?
% this is described in the following paragraph, should we merge them
% (bc there are also no sub-RQs now) or is it close enough? :)
For each repository in \emph{LogChunks}, we split the examples
chronologically into training and test set.
Therefore, we train on
examples from past build logs and test on more recent build logs.

@@

% Recall and precision of CTS and KWS vary with the number of lines
% selected for retrieval.
% We evaluate the effect of varying the number
% of extracted lines by multiplying the average number of lines
% present in the training examples with a \emph{retrieval size factor}
% from 0.5 to 2.5 in steps of 0.5.

@@

% % The averaged precision, recall and F$_{1}$-score f all techniques is
% % compared in Figure~\ref{fig:recall-precision-all}.
% The recall of PBE
% % has a high skew towards one and zero, meaning in most cases either
% % the retrieval is successful or no relevant lines are extracted at
% % all.
% PBE has the highest average precision with 95\%.
% Chunk
% % retrieval with CTS has the highest average F$_{1}$-score with 51\%
% % and the second highest recall with 46\%.
% KWS has the smallest
% % precision of the three chunk retrieval techniques.
% With 16\% it is
% % still higher than the precision of the RLR baseline with 7\%.
% KWS
% % has the highest recall of all techniques with 70\%.

@@

\section{Future Work}
% TODO: survey build logs tools in industry
